Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-05 WSSSPE3/report/WSSSPE3_review.tex

\item \textbf{Jeffrey Carver: \textit{On the Need for Software Engineering Support for
Sustainable Scientic Software}}
I argue that for scientific software to be truly sustainable, there is a need
for developers to use appropriate software engineering practices. My experience
interacting with scientific teams indicates that choosing and tailoring these
practices is not a trivial exercise. There is a general culture clash between
software engineering and science that hinders our ability to communicate and
choose appropriate methods. In addition, many experience scientific software
developers appear to be unaware of software engineering practices that may be
beneficial to them. The most appropriate software engineering practices are
those that are lightweight, properly tailored, and focus on the key software
development problems faced by scientists. In order to increase the use of
software engineering in science, we need more documented success stories. These
successes need to be socialized within the scientific community through
workshops like the Software Engineering for Science workshop
series~\footnote{\href{http://www.SE4Science.org/workshops}{http://www.SE4Science.org/workshops}}
and the new Software Engineering track in Computing in Science and Engineering
magazine.

>>>>

\item \textbf{Jeffrey Carver: \textit{On the Need for Software Engineering Support for
Sustainable Scientic Software}}
Jeff argued that for scientific software to be truly sustainable, there is a need
for developers to use appropriate software engineering practices. His experience
interacting with scientific teams indicates that choosing and tailoring these
practices is not a trivial exercise. There is a general culture clash between
software engineering and science that hinders our ability to communicate and
choose appropriate methods. In addition, many experience scientific software
developers appear to be unaware of software engineering practices that may be
beneficial to them. The most appropriate software engineering practices are
those that are lightweight, properly tailored, and focus on the key software
development problems faced by scientists. In order to increase the use of
software engineering in science, we need more documented success stories. These
successes need to be socialized within the scientific community through
workshops like the Software Engineering for Science workshop
series\footnote{\href{http://www.SE4Science.org/workshops}{http://www.SE4Science.org/workshops}}
and the new Software Engineering track in
\textit{Computing in Science and Engineering} magazine.
